Do More Polling Locations in Wards Increase Turnout? An Analysis of the 2022 Toronto Municipal Election

### 2023-05-23 outputs/paper/paper.qmd
Installed and loaded a number of required packages

---
title: "Do More Polling Locations in Wards Increase Turnout? An Analysis of the 2022 Toronto Municipal Election"
author: "Inessa De Angelis"
thanks: "Code and data from this analysis are available at: https://github.com/InessaDeAngelis/Toronto_Elections."
date: "`r Sys.time()`"
date-format: "22 05 2023"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: ref.bib
---

>>>>

---
title: "Do More Polling Locations in Wards Increase Turnout? An Analysis of the 2022 Toronto Municipal Election"
author: "Inessa De Angelis"
thanks: "Code and data from this analysis are available at: https://github.com/InessaDeAngelis/Toronto_Elections."
date: "`r Sys.time()`"
date-format: "25 05 2023"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: ref.bib
---
